Intelligent Building Energy Management System

### 2021-05-08 parts/40-ExperimentalResults.tex
Updated file paths and added figures

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.5]{figs/BEMS_GUI_Linux.png}
    \caption{Desktop GUI}
    \label{fig:desktopgui}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.5]{figs/BEMS_GUI_Linux_Warning.png}
    \caption{Popup Error}
    \label{fig:popuperror}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.5]{figs/Login.png}
    \caption{Login Page}
    \label{fig:Home_screen}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.35]{figs/Home_screen.png}
    \caption{Home Page}
    \label{fig:Home_screen}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.35]{figs/ActiveDevices_screen.png}
    \caption{Active Devices Page}
    \label{fig:active_devices}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.35]{figs/ActiveDevices_plot.png}
    \caption{Active Devices Plot}
    \label{fig:active_devices_plot}
\end{figure}

After clicking \say{View Status Plots}, a modal will pop up for the user to further
interact with. By default, power usage data points for the current day are
loaded at first, but another day can be selected by clicking on the calendar
icon in the lower right corner. The plot is then updated by clicking \say{Update
Plots}. This is done by collecting data from the Apache Cassandra database and
simply plotting all the points found for the specified day. Underneath the plot,
the total energy consumed for the specified day is displayed. That total energy
is found using the trapezoid method for integration on the plot. %
%
\begin{figure}
    \centering
    \includegraphics[scale=0.35]{figs/Applications_screen.png}
    \caption{Scheduling Page}
    \label{fig:schedulingl}
\end{figure}
%

>>>>

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.5]{figs/GUI/BEMS_GUI_Linux.png}
    \caption{Desktop GUI}
    \label{fig:desktopgui}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.5]{figs/GUI/BEMS_GUI_Linux_Warning.png}
    \caption{Popup Error}
    \label{fig:popuperror}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.5]{figs/webServer/Login.png}
    \caption{Login Page}
    \label{fig:Home_screen}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.35]{figs/webServer/Home_screen.png}
    \caption{Home Page}
    \label{fig:Home_screen}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.35]{figs/webServer/ActiveDevices_screen.png}
    \caption{Active Devices Page}
    \label{fig:active_devices}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.35]{figs/webServer/ActiveDevices_plot.png}
    \caption{Active Devices Plot}
    \label{fig:active_devices_plot}
\end{figure}

After clicking \say{View Status Plots}, a modal will pop up for the user to further
interact with. By default, power usage data points for the current day are
loaded at first, but another day can be selected by clicking on the calendar
icon in the lower right corner. The plot is then updated by clicking \say{Update
Plots}. This is done by collecting data from the Apache Cassandra database and
simply plotting all the points found for the specified day. Underneath the plot,
the total energy consumed for the specified day is displayed. That total energy
is found using the trapezoid method for integration on the plot. %
%
\begin{figure}
    \centering
    \includegraphics[scale=0.35]{figs/webServer/Applications_screen.png}
    \caption{Scheduling Page}
    \label{fig:schedulingl}
\end{figure}
%
